---
title: 'Ensembles `r paste(format(Sys.time(),"%Y-%m-%d %H:%M:%S") , commandArgs(trailingOnly=T)[1])` + Norms 1991-2020 (Reana NCEP)'
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    lightbox: true
    theme: united
---

```{r setup, include=FALSE}

# commandArgs(trailingOnly=T)[1] Location Name
# commandArgs(trailingOnly=T)[2] Profile Name
# commandArgs(trailingOnly=T)[3] Date YYYYMMDD
# commandArgs(trailingOnly=T)[4] TZ

prof_name = commandArgs(trailingOnly = T)[2]
date_var = as.Date(commandArgs(trailingOnly = T)[3],"%Y%m%d")
the_tz = commandArgs(trailingOnly = T)[4]

library(flexdashboard)
library(lubridate)
library(DescTools)
library(spatstat.utils)
library(scales)
library(ggplot2)

library(TSrepr)
library(data.table)
library(cluster)
library(clusterCrit)
library(zoo)
library(RColorBrewer)

library(stringr)
library(reshape)
library(ggpubr)
library(gridExtra)

library(attempt)
library(dplyr)
```

```{r load_data}

norms_df <- read.csv(sprintf("../../assets/norms_%s/norms_df_%s.csv", prof_name, prof_name))

norms_df_past <- norms_df
norms_df_now <- norms_df
norms_df_future <- norms_df

norms_df_past$date <- paste0(format(date_var-years(1), "%Y"),"-",norms_df$subdate)
norms_df_now$date <- paste0(format(date_var, "%Y"),"-",norms_df$subdate)
norms_df_future$date <- paste0(format(date_var+years(1), "%Y"),"-",norms_df$subdate)

if (!leap_year(date_var-years(1)))
{
  norms_df_past <- norms_df_past[-which(grepl("02-29",norms_df_past$date)),]
}

if (!leap_year(date_var))
{
  norms_df_now<- norms_df_now[-which(grepl("02-29",norms_df_now$date)),]
}

if (!leap_year(date_var+years(1)))
{
  norms_df_future <- norms_df_future[-which(grepl("02-29",norms_df_future$date)),]
}

norms_profile <- 
  merge(norms_df_past,
        norms_df_now,
        all.x = TRUE,
        all.y = TRUE)

norms_profile <- 
  merge(norms_profile,
        norms_df_future,
        all.x = TRUE,
        all.y = TRUE)

norms_profile$subdate <- NULL
norms_profile$date <- as_datetime(norms_profile$date) + hours(3)

z500_cols <- read.csv("../../assets/norms/dam.csv", quote = "'")

t850_cols <- read.csv("../../assets/norms/temp.csv", quote = "'")

t2m_cols <- read.csv("../../assets/norms/t2m.csv", quote = "'")

pp_cols <- read.csv("../../assets/norms/pp.csv", quote = "'")
names(pp_cols) <- gsub('X', '', names(pp_cols))

trans_axes <- function(orig) {
  new <- (orig * 7 / 3) - 30
  return(new)
}

trans_axes_tsol <- function(orig) {
  new <- (orig * 7 / 3) - 20
  return(new)
}


barwidth = c(rep(2, 40), rep(4, 36))
barwidth_ai = c(rep(4, 56))
barwidth_gefs = c(rep(2, 56), rep(4, 28))
barwidth_ifs = c(rep(2, 40), rep(4, 36))



get_data <- function(date, model) {
  if (model == "ifs") {
    model_old = "ecmwf"
  } else {
    model_old = model
  }
  if (file.exists(sprintf("../../data/%s/%s-%s.csv", model, model, date))) {
    thetable <-
      read.csv(sprintf("../../data/%s/%s-%s.csv", model, model, date))
  } else  if (file.exists(sprintf("../../data/%s/%s-%s.csv", model, model_old, date))) {
    thetable <-
      read.csv(sprintf("../../data/%s/%s-%s.csv", model, model, date))
  } else {
    thetable <- as.data.frame(t(c(NA, NA, NA, NA, NA, NA, NA)))
  }
  
  if (nrow(thetable) == 0) {
    thetable <- as.data.frame(t(c(NA, NA, NA, NA, NA, NA, NA)))
  }
  
  names(thetable) <-
    c("runs",
      "dates",
      "profile",
      "geop",
      "tempalt",
      "tempsol",
      "precs")
  thetable$runs <- paste(toupper(model), thetable$runs)
  return(thetable)
}


```






```{r load_data2}
allruns <- get_data(str_replace_all(date_var, "-", ""), "gefs")
allruns <-
  merge(allruns,
        get_data(str_replace_all(date_var, "-", ""), "gem"),
        all.x = TRUE,
        all.y = TRUE)
allruns <-
  merge(allruns,
        get_data(str_replace_all(date_var, "-", ""), "aigefs"),
        all.x = TRUE,
        all.y = TRUE)
allruns <-
  merge(allruns,
        get_data(str_replace_all(date_var, "-", ""), "ifs"),
        all.x = TRUE,
        all.y = TRUE)
allruns <-
  merge(allruns,
        get_data(str_replace_all(date_var, "-", ""), "aifs"),
        all.x = TRUE,
        all.y = TRUE)

allruns <- allruns[order(allruns$dates), ]
allruns <- allruns[which(allruns$profile == prof_name), ]
allruns <- allruns[, -c(3)]

allruns$dates = paste(allruns$dates,"UTC")
the_dates <- sort(unique(allruns$dates))

the_dates <-
  the_dates[(the_dates >  as_datetime(sprintf("%s 21:00:00", date_var)))]

the_dates <-
  the_dates[(the_dates < format(as_datetime(the_dates[1]) + days(14),"%Y-%m-%d %H:%M:%S"))]
```







```{r load_pp}

pp_unif <- allruns[, c(1, 2, 6)]
pp_unif <- na.omit(pp_unif)
names(pp_unif) <- c("runs", "variable", "value")

maps_limits <-
  c(as.character(seq(0, 0.9, 0.1)), as.character(seq(1, 100)))

pp_unif_gefs <- pp_unif[which(grepl("^GEFS", pp_unif$runs)),]

pp_unif_gem <- pp_unif[which(grepl("^GEM", pp_unif$runs)),]

pp_unif_noaa <- pp_unif[which(grepl("^GEFS", pp_unif$runs) | grepl("^GEM", pp_unif$runs)),]
pp_unif_allnoaa <- pp_unif[which(grepl("GEFS", pp_unif$runs) | grepl("^GEM", pp_unif$runs)),]

pp_unif_aigefs <- pp_unif[which(grepl("^AIGEFS", pp_unif$runs)),]

pp_unif_allgefs <- pp_unif[which(grepl("GEFS", pp_unif$runs)),]


pp_unif_ifs <- pp_unif[which(grepl("^IFS", pp_unif$runs)),]
pp_unif_aifs <- pp_unif[which(grepl("^AIFS", pp_unif$runs)),]
pp_unif_allifs <- pp_unif[which(grepl("IFS", pp_unif$runs)),]


pp_unif_noai <- pp_unif[which(grepl("^IFS", pp_unif$runs)
                              |grepl("^GEFS", pp_unif$runs)
                              |grepl("^GEM", pp_unif$runs)
                              ),]


pp_unif <- pp_unif[order(pp_unif$runs),]


for (i in seq(1,nrow(pp_unif))){
    # if (as.POSIXct(pp_unif$variable[i]) > as.POSIXct(date_var) + hours(144)) {
      if (as.integer(format(as.POSIXct(pp_unif$variable[i]),"%H"))  %in% seq(3,21,6) ) {
        pp_unif$value[i-1] = pp_unif$value[i-1] + pp_unif$value[i] 
      }
    # }
}

pp_unif <- pp_unif[-which(#as.POSIXct(pp_unif$variable) > as.POSIXct(date_var) + hours(144) &
                            as.integer(format(as.POSIXct(pp_unif$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]





pp_unif_gefs <- pp_unif_gefs[order(pp_unif_gefs$runs),]

for (i in seq(1,nrow(pp_unif_gefs))){
    if (as.POSIXct(pp_unif_gefs$variable[i]) > as.POSIXct(date_var) + hours(192)) {
      if (as.integer(format(as.POSIXct(pp_unif_gefs$variable[i]),"%H"))  %in% seq(3,21,6) ) {
        pp_unif_gefs$value[i-1] = pp_unif_gefs$value[i-1] + pp_unif_gefs$value[i] 
      }
    }
}

pp_unif_gefs <- pp_unif_gefs[-which(as.POSIXct(pp_unif_gefs$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC") > as.POSIXct(date_var) + hours(192) & as.integer(format(as.POSIXct(pp_unif_gefs$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]





pp_unif_gem <- pp_unif_gem[order(pp_unif_gem$runs),]

for (i in seq(1,nrow(pp_unif_gem))){
    if (as.POSIXct(pp_unif_gem$variable[i]) > as.POSIXct(date_var) + hours(192)) {
      if (as.integer(format(as.POSIXct(pp_unif_gem$variable[i],"%H")))  %in% seq(3,21,6) ) {
        pp_unif_gem$value[i-1] = pp_unif_gem$value[i-1] + pp_unif_gem$value[i] 
      }
    }
}

pp_unif_gem <- pp_unif_gem[-which(as.POSIXct(pp_unif_gem$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC") > as.POSIXct(date_var) + hours(192) & as.integer(format(as.POSIXct(pp_unif_gem$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]





pp_unif_noaa <- pp_unif_noaa[order(pp_unif_noaa$runs),]

for (i in seq(1,nrow(pp_unif_noaa))){
    if (as.POSIXct(pp_unif_noaa$variable[i]) > as.POSIXct(date_var) + hours(192)) {
      if (as.integer(format(as.POSIXct(pp_unif_noaa$variable[i]),"%H"))  %in% seq(3,21,6) ) {
        pp_unif_noaa$value[i-1] = pp_unif_noaa$value[i-1] + pp_unif_noaa$value[i] 
      }
    }
}

pp_unif_noaa <- pp_unif_noaa[-which(as.POSIXct(pp_unif_noaa$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC") > as.POSIXct(date_var) + hours(192) & as.integer(format(as.POSIXct(pp_unif_noaa$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]





pp_unif_allnoaa <- pp_unif_allnoaa[order(pp_unif_allnoaa$runs),]

for (i in seq(1,nrow(pp_unif_allnoaa))){
    #if (as.POSIXct(pp_unif_allnoaa$variable[i]) > as.POSIXct(date_var) + hours(192)) {
      if (as.integer(format(as.POSIXct(pp_unif_allnoaa$variable[i]),"%H"))  %in% seq(3,21,6) ) {
        pp_unif_allnoaa$value[i-1] = pp_unif_allnoaa$value[i-1] + pp_unif_allnoaa$value[i] 
      }
    #}
}

pp_unif_allnoaa <- pp_unif_allnoaa[-which(#as.POSIXct(pp_unif_allnoaa$variable) > as.POSIXct(date_var) + hours(192) &
  as.integer(format(as.POSIXct(pp_unif_allnoaa$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]





pp_unif_aigefs <- pp_unif_aigefs[order(pp_unif_aigefs$runs),]
# 
# for (i in seq(1,nrow(pp_unif_aigefs))){
#     # if (as.POSIXct(pp_unif_aigefs$variable[i]) > as.POSIXct(date_var) + hours(192)) {
#       if (as.integer(format(as.POSIXct(pp_unif_aigefs$variable[i]),"%H"))  %in% seq(3,21,6) ) {
#         pp_unif_aigefs$value[i-1] = pp_unif_aigefs$value[i-1] + pp_unif_aigefs$value[i] 
#       }
#     # }
# }
# 
# pp_unif_aigefs <- pp_unif_aigefs[which(as.POSIXct(pp_unif_aigefs$variable) > as.POSIXct(date_var) + hours(0) 
#                                           & as.integer(format(as.POSIXct(pp_unif_aigefs$variable),"%H"))  %in% seq(3,21,6)
#                                         ),]





pp_unif_allgefs <- pp_unif_allgefs[order(pp_unif_allgefs$runs),]

for (i in seq(1,nrow(pp_unif_allgefs))){
    # if (as.POSIXct(pp_unif_allgefs$variable[i]) > as.POSIXct(date_var) + hours(192)) {
      if (as.integer(format(as.POSIXct(pp_unif_allgefs$variable[i]),"%H"))  %in% seq(3,21,6) ) {
        pp_unif_allgefs$value[i-1] = pp_unif_allgefs$value[i-1] + pp_unif_allgefs$value[i] 
      }
    # }
}

pp_unif_allgefs <- pp_unif_allgefs[-which(#as.POSIXct(pp_unif_allgefs$variable) > as.POSIXct(date_var) + hours(192) &
                                            as.integer(format(as.POSIXct(pp_unif_allgefs$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]




pp_unif_ifs <- pp_unif_ifs[order(pp_unif_ifs$runs),]

for (i in seq(1,nrow(pp_unif_ifs))){
    if (as.POSIXct(pp_unif_ifs$variable[i]) > as.POSIXct(date_var) + hours(144)) {
      if (as.integer(format(as.POSIXct(pp_unif_ifs$variable[i]),"%H"))  %in% seq(3,21,6) ) {
        pp_unif_ifs$value[i-1] = pp_unif_ifs$value[i-1] + pp_unif_ifs$value[i] 
      }
    }
}

pp_unif_ifs <- pp_unif_ifs[-which(as.POSIXct(pp_unif_ifs$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC") > as.POSIXct(date_var) + hours(144) & as.integer(format(as.POSIXct(pp_unif_ifs$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]






pp_unif_aifs <- pp_unif_aifs[order(pp_unif_aifs$runs),]
# 
# for (i in seq(1,nrow(pp_unif_aifs))){
#     # if (as.POSIXct(pp_unif_aifs$variable[i]) > as.POSIXct(date_var) + hours(144)) {
#       if (as.integer(format(as.POSIXct(pp_unif_aifs$variable[i]),"%H"))  %in% seq(3,21,6) ) {
#         pp_unif_aifs$value[i-1] = pp_unif_aifs$value[i-1] + pp_unif_aifs$value[i] 
#       }
#     # }
# }
# 
# pp_unif_aifs <- pp_unif_aifs[-which(#as.POSIXct(pp_unif_aifs$variable) > as.POSIXct(date_var) + hours(144) &
#                                       as.integer(format(as.POSIXct(pp_unif_aifs$variable),"%H"))  %in% seq(3,21,6)),]
# 
# 




pp_unif_allifs <- pp_unif_allifs[order(pp_unif_allifs$runs),]

for (i in seq(1,nrow(pp_unif_allifs))){
    # if (as.POSIXct(pp_unif_allifs$variable[i]) > as.POSIXct(date_var) + hours(144)) {
      if (as.integer(format(as.POSIXct(pp_unif_allifs$variable[i]),"%H"))  %in% seq(3,21,6) ) {
        pp_unif_allifs$value[i-1] = pp_unif_allifs$value[i-1] + pp_unif_allifs$value[i] 
      }
    # }
}

pp_unif_allifs <- pp_unif_allifs[-which(#as.POSIXct(pp_unif_allifs$variable) > as.POSIXct(date_var) + hours(144) &
                                          as.integer(format(as.POSIXct(pp_unif_allifs$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]




pp_unif_noai <- pp_unif_noai[order(pp_unif_noai$runs),]

for (i in seq(1,nrow(pp_unif_noai))){
    if (as.POSIXct(pp_unif_noai$variable[i]) > as.POSIXct(date_var) + hours(144)) {
      if (as.integer(format(as.POSIXct(pp_unif_noai$variable[i]),"%H"))  %in% seq(3,21,6) ) {

        pp_unif_noai$value[i-1] = pp_unif_noai$value[i-1] + pp_unif_noai$value[i]
      }
    }
}

pp_unif_noai <- pp_unif_noai[-which(as.POSIXct(pp_unif_noai$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC") > as.POSIXct(date_var) + hours(144) & as.integer(format(as.POSIXct(pp_unif_noai$variable,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]











pp_unif$value[which(pp_unif$value < 1)] <-
  round(pp_unif$value[which(pp_unif$value < 1)], 1)
pp_unif$value[which(pp_unif$value > 1)] <-
  round_any(pp_unif$value[which(pp_unif$value > 1)], 1)
pp_unif$value[which(pp_unif$value > 30)] <- 30



pp_unif_gefs$value[which(pp_unif_gefs$value < 1)] <-
  round(pp_unif_gefs$value[which(pp_unif_gefs$value < 1)], 1)
pp_unif_gefs$value[which(pp_unif_gefs$value > 1)] <-
  round_any(pp_unif_gefs$value[which(pp_unif_gefs$value > 1)], 1)
pp_unif_gefs$value[which(pp_unif_gefs$value > 30)] <- 30



pp_unif_gem$value[which(pp_unif_gem$value < 1)] <-
  round(pp_unif_gem$value[which(pp_unif_gem$value < 1)], 1)
pp_unif_gem$value[which(pp_unif_gem$value > 1)] <-
  round_any(pp_unif_gem$value[which(pp_unif_gem$value > 1)], 1)
pp_unif_gem$value[which(pp_unif_gem$value > 30)] <- 30



pp_unif_aigefs$value[which(pp_unif_aigefs$value < 1)] <-
  round(pp_unif_aigefs$value[which(pp_unif_aigefs$value < 1)], 1)
pp_unif_aigefs$value[which(pp_unif_aigefs$value > 1)] <-
  round_any(pp_unif_aigefs$value[which(pp_unif_aigefs$value > 1)], 1)
pp_unif_aigefs$value[which(pp_unif_aigefs$value > 30)] <- 30



pp_unif_allgefs$value[which(pp_unif_allgefs$value < 1)] <-
  round(pp_unif_allgefs$value[which(pp_unif_allgefs$value < 1)], 1)
pp_unif_allgefs$value[which(pp_unif_allgefs$value > 1)] <-
  round_any(pp_unif_allgefs$value[which(pp_unif_allgefs$value > 1)], 1)
pp_unif_allgefs$value[which(pp_unif_allgefs$value > 30)] <- 30



pp_unif_ifs$value[which(pp_unif_ifs$value < 1)] <-
  round(pp_unif_ifs$value[which(pp_unif_ifs$value < 1)], 1)
pp_unif_ifs$value[which(pp_unif_ifs$value > 1)] <-
  round_any(pp_unif_ifs$value[which(pp_unif_ifs$value > 1)], 1)
pp_unif_ifs$value[which(pp_unif_ifs$value > 30)] <- 30



pp_unif_aifs$value[which(pp_unif_aifs$value < 1)] <-
  round(pp_unif_aifs$value[which(pp_unif_aifs$value < 1)], 1)
pp_unif_aifs$value[which(pp_unif_aifs$value > 1)] <-
  round_any(pp_unif_aifs$value[which(pp_unif_aifs$value > 1)], 1)
pp_unif_aifs$value[which(pp_unif_aifs$value > 30)] <- 30



pp_unif_allifs$value[which(pp_unif_allifs$value < 1)] <-
  round(pp_unif_allifs$value[which(pp_unif_allifs$value < 1)], 1)
pp_unif_allifs$value[which(pp_unif_allifs$value > 1)] <-
  round_any(pp_unif_allifs$value[which(pp_unif_allifs$value > 1)], 1)
pp_unif_allifs$value[which(pp_unif_allifs$value > 30)] <- 30



pp_unif_noaa$value[which(pp_unif_noaa$value < 1)] <-
  round(pp_unif_noaa$value[which(pp_unif_noaa$value < 1)], 1)
pp_unif_noaa$value[which(pp_unif_noaa$value > 1)] <-
  round_any(pp_unif_noaa$value[which(pp_unif_noaa$value > 1)], 1)
pp_unif_noaa$value[which(pp_unif_noaa$value > 30)] <- 30



pp_unif_allnoaa$value[which(pp_unif_allnoaa$value < 1)] <-
  round(pp_unif_allnoaa$value[which(pp_unif_allnoaa$value < 1)], 1)
pp_unif_allnoaa$value[which(pp_unif_allnoaa$value > 1)] <-
  round_any(pp_unif_allnoaa$value[which(pp_unif_allnoaa$value > 1)], 1)
pp_unif_allnoaa$value[which(pp_unif_allnoaa$value > 30)] <- 30



pp_unif_noai$value[which(pp_unif_noai$value < 1)] <-
  round(pp_unif_noai$value[which(pp_unif_noai$value < 1)], 1)
pp_unif_noai$value[which(pp_unif_noai$value > 1)] <-
  round_any(pp_unif_noai$value[which(pp_unif_noai$value > 1)], 1)
pp_unif_noai$value[which(pp_unif_noai$value > 30)] <- 30







pp_props_all <-
  prop.table(table(pp_unif[, "variable"], pp_unif[, "value"]), margin =
               1)
manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_all))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_all <- cbind(pp_props_all, rep(0, nrow(pp_props_all)))
    colnames(pp_props_all)[length(colnames(pp_props_all))] <- var
  }
  
}
pp_props_all <- pp_props_all[, as.character(maps_limits)]
pp_probs_all = t(apply(pp_props_all, 1, revcumsum))
colnames(pp_probs_all) <- colnames(pp_props_all)
pp_probs_all <- as.data.frame.matrix(pp_probs_all)
pp_probs_all[, 1] <- row.names(pp_probs_all)
pp_probs_all <- pp_probs_all[, as.character(maps_limits)]
names(pp_probs_all) <- paste(rep("V", 110), seq(1, 110), sep = "")







pp_props_noai <-
  prop.table(table(pp_unif_noai[, "variable"], pp_unif_noai[, "value"]), margin =
               1)
manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_noai))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_noai <- cbind(pp_props_noai, rep(0, nrow(pp_props_noai)))
    colnames(pp_props_noai)[length(colnames(pp_props_noai))] <- var
  }
  
}
pp_props_noai <- pp_props_noai[, as.character(maps_limits)]
pp_probs_noai = t(apply(pp_props_noai, 1, revcumsum))
colnames(pp_probs_noai) <- colnames(pp_props_noai)
pp_probs_noai <- as.data.frame.matrix(pp_probs_noai)
pp_probs_noai[, 1] <- row.names(pp_probs_noai)
pp_probs_noai <- pp_probs_noai[, as.character(maps_limits)]
names(pp_probs_noai) <- paste(rep("V", 110), seq(1, 110), sep = "")







pp_props_gefs <-
  prop.table(table(pp_unif_gefs$variable, pp_unif_gefs$value), margin =
               1)

pp_props_gefs[which(is.na(pp_props_gefs))] = 0

manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_gefs))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_gefs <- cbind(pp_props_gefs, rep(0, nrow(pp_props_gefs)))
    colnames(pp_props_gefs)[length(colnames(pp_props_gefs))] <- var
  }
  
}
pp_props_gefs <- pp_props_gefs[, as.character(maps_limits)]


pp_probs_gefs = t(apply(pp_props_gefs, 1, revcumsum))
colnames(pp_probs_gefs) <- colnames(pp_props_gefs)
pp_probs_gefs <- as.data.frame.matrix(pp_probs_gefs)
pp_probs_gefs[, 1] <- row.names(pp_probs_gefs)
pp_probs_gefs <- pp_probs_gefs[, as.character(maps_limits)]
names(pp_probs_gefs) <- paste(rep("V", 110), seq(1, 110), sep = "")







pp_props_aigefs <-
  prop.table(table(pp_unif_aigefs$variable, pp_unif_aigefs$value), margin =
               1)

pp_props_aigefs[which(is.na(pp_props_aigefs))] = 0

manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_aigefs))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_aigefs <- cbind(pp_props_aigefs, rep(0, nrow(pp_props_aigefs)))
    colnames(pp_props_aigefs)[length(colnames(pp_props_aigefs))] <- var
  }
  
}
pp_props_aigefs <- pp_props_aigefs[, as.character(maps_limits)]


pp_probs_aigefs = t(apply(pp_props_aigefs, 1, revcumsum))
colnames(pp_probs_aigefs) <- colnames(pp_props_aigefs)
pp_probs_aigefs <- as.data.frame.matrix(pp_probs_aigefs)
pp_probs_aigefs[, 1] <- row.names(pp_probs_aigefs)
pp_probs_aigefs <- pp_probs_aigefs[, as.character(maps_limits)]
names(pp_probs_aigefs) <- paste(rep("V", 110), seq(1, 110), sep = "")







pp_props_allgefs <-
  prop.table(table(pp_unif_allgefs$variable, pp_unif_allgefs$value), margin =
               1)

pp_props_allgefs[which(is.na(pp_props_allgefs))] = 0

manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_allgefs))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_allgefs <- cbind(pp_props_allgefs, rep(0, nrow(pp_props_allgefs)))
    colnames(pp_props_allgefs)[length(colnames(pp_props_allgefs))] <- var
  }
  
}
pp_props_allgefs <- pp_props_allgefs[, as.character(maps_limits)]


pp_probs_allgefs = t(apply(pp_props_allgefs, 1, revcumsum))
colnames(pp_probs_allgefs) <- colnames(pp_props_allgefs)
pp_probs_allgefs <- as.data.frame.matrix(pp_probs_allgefs)
pp_probs_allgefs[, 1] <- row.names(pp_probs_allgefs)
pp_probs_allgefs <- pp_probs_allgefs[, as.character(maps_limits)]
names(pp_probs_allgefs) <- paste(rep("V", 110), seq(1, 110), sep = "")







pp_props_ifs <-
  prop.table(table(pp_unif_ifs$variable, pp_unif_ifs$value), margin =
               1)

pp_props_ifs[which(is.na(pp_props_ifs))] = 0

manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_ifs))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_ifs <- cbind(pp_props_ifs, rep(0, nrow(pp_props_ifs)))
    colnames(pp_props_ifs)[length(colnames(pp_props_ifs))] <- var
  }
  
}
pp_props_ifs <- pp_props_ifs[, as.character(maps_limits)]


pp_probs_ifs = t(apply(pp_props_ifs, 1, revcumsum))
colnames(pp_probs_ifs) <- colnames(pp_props_ifs)
pp_probs_ifs <- as.data.frame.matrix(pp_probs_ifs)
pp_probs_ifs[, 1] <- row.names(pp_probs_ifs)
pp_probs_ifs <- pp_probs_ifs[, as.character(maps_limits)]
names(pp_probs_ifs) <- paste(rep("V", 110), seq(1, 110), sep = "")



pp_props_aifs <-
  prop.table(table(pp_unif_aifs$variable, pp_unif_aifs$value), margin =
               1)

pp_props_aifs[which(is.na(pp_props_aifs))] = 0

manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_aifs))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_aifs <- cbind(pp_props_aifs, rep(0, nrow(pp_props_aifs)))
    colnames(pp_props_aifs)[length(colnames(pp_props_aifs))] <- var
  }
  
}
pp_props_aifs <- pp_props_aifs[, as.character(maps_limits)]


pp_probs_aifs = t(apply(pp_props_aifs, 1, revcumsum))
colnames(pp_probs_aifs) <- colnames(pp_props_aifs)
pp_probs_aifs <- as.data.frame.matrix(pp_probs_aifs)
pp_probs_aifs[, 1] <- row.names(pp_probs_aifs)
pp_probs_aifs <- pp_probs_aifs[, as.character(maps_limits)]
names(pp_probs_aifs) <- paste(rep("V", 110), seq(1, 110), sep = "")



pp_props_allifs <-
  prop.table(table(pp_unif_allifs$variable, pp_unif_allifs$value), margin =
               1)

pp_props_allifs[which(is.na(pp_props_allifs))] = 0

manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_allifs))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_allifs <- cbind(pp_props_allifs, rep(0, nrow(pp_props_allifs)))
    colnames(pp_props_allifs)[length(colnames(pp_props_allifs))] <- var
  }
  
}
pp_props_allifs <- pp_props_allifs[, as.character(maps_limits)]


pp_probs_allifs = t(apply(pp_props_allifs, 1, revcumsum))
colnames(pp_probs_allifs) <- colnames(pp_props_allifs)
pp_probs_allifs <- as.data.frame.matrix(pp_probs_allifs)
pp_probs_allifs[, 1] <- row.names(pp_probs_allifs)
pp_probs_allifs <- pp_probs_allifs[, as.character(maps_limits)]
names(pp_probs_allifs) <- paste(rep("V", 110), seq(1, 110), sep = "")








pp_props_noaa <-
  prop.table(table(pp_unif_noaa$variable, pp_unif_noaa$value), margin =
               1)

pp_props_noaa[which(is.na(pp_props_noaa))] = 0

manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_noaa))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_noaa <- cbind(pp_props_noaa, rep(0, nrow(pp_props_noaa)))
    colnames(pp_props_noaa)[length(colnames(pp_props_noaa))] <- var
  }
  
}
pp_props_noaa <- pp_props_noaa[, as.character(maps_limits)]


pp_probs_noaa = t(apply(pp_props_noaa, 1, revcumsum))
colnames(pp_probs_noaa) <- colnames(pp_props_noaa)
pp_probs_noaa <- as.data.frame.matrix(pp_probs_noaa)
pp_probs_noaa[, 1] <- row.names(pp_probs_noaa)
pp_probs_noaa <- pp_probs_noaa[, as.character(maps_limits)]
names(pp_probs_noaa) <- paste(rep("V", 110), seq(1, 110), sep = "")









pp_props_allnoaa <-
  prop.table(table(pp_unif_allnoaa$variable, pp_unif_allnoaa$value), margin =
               1)

pp_props_allnoaa[which(is.na(pp_props_allnoaa))] = 0

manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_allnoaa))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_allnoaa <- cbind(pp_props_allnoaa, rep(0, nrow(pp_props_allnoaa)))
    colnames(pp_props_allnoaa)[length(colnames(pp_props_allnoaa))] <- var
  }
  
}
pp_props_allnoaa <- pp_props_allnoaa[, as.character(maps_limits)]


pp_probs_allnoaa = t(apply(pp_props_allnoaa, 1, revcumsum))
colnames(pp_probs_allnoaa) <- colnames(pp_props_allnoaa)
pp_probs_allnoaa <- as.data.frame.matrix(pp_probs_allnoaa)
pp_probs_allnoaa[, 1] <- row.names(pp_probs_allnoaa)
pp_probs_allnoaa <- pp_probs_allnoaa[, as.character(maps_limits)]
names(pp_probs_allnoaa) <- paste(rep("V", 110), seq(1, 110), sep = "")









pp_props_gem <-
  prop.table(table(pp_unif_gem$variable, pp_unif_gem$value), margin =
               1)

pp_props_gem[which(is.na(pp_props_gem))] = 0

manquants <-
  maps_limits[which(is.na(match(maps_limits, colnames(pp_props_gem))))]
if (length(manquants  > 0)) {
  for (var in manquants) {
    pp_props_gem <- cbind(pp_props_gem, rep(0, nrow(pp_props_gem)))
    colnames(pp_props_gem)[length(colnames(pp_props_gem))] <- var
  }
  
}
pp_props_gem <- pp_props_gem[, as.character(maps_limits)]


pp_probs_gem = t(apply(pp_props_gem, 1, revcumsum))
colnames(pp_probs_gem) <- colnames(pp_props_gem)
pp_probs_gem <- as.data.frame.matrix(pp_probs_gem)
pp_probs_gem[, 1] <- row.names(pp_probs_gem)
pp_probs_gem <- pp_probs_gem[, as.character(maps_limits)]
names(pp_probs_gem) <- paste(rep("V", 110), seq(1, 110), sep = "")



```




```{r load_pp2}


plotruns <- allruns[, c(1, 2, 3, 4, 5)]
plotruns$geop <- round_any(plotruns$geop, 0.1)
plotruns$tempalt <- round_any(plotruns$tempalt, 0.1)
plotruns$tempsol <- round_any(plotruns$tempsol, 0.1)








plotruns <- plotruns[which(plotruns$dates >= the_dates[1]), ]
plotruns <- plotruns[which(plotruns$dates <= the_dates[length(the_dates)]),]

pp_probs_all <-
  pp_probs_all[which(row.names(pp_probs_all) >= the_dates[1]), ]
pp_probs_all <-
  pp_probs_all[which(row.names(pp_probs_all) <= the_dates[length(the_dates)]),]


pp_probs_gefs <-
  pp_probs_gefs[which(row.names(pp_probs_gefs) >= the_dates[1]), ]
pp_probs_gefs <-
  pp_probs_gefs[which(row.names(pp_probs_gefs) <= the_dates[length(the_dates)]),]


pp_probs_aigefs <-
  pp_probs_aigefs[which(row.names(pp_probs_aigefs) >= the_dates[1]), ]
pp_probs_aigefs <-
  pp_probs_aigefs[which(row.names(pp_probs_aigefs) <= the_dates[length(the_dates)]),]


pp_probs_allgefs <-
  pp_probs_allgefs[which(row.names(pp_probs_allgefs) >= the_dates[1]), ]
pp_probs_allgefs <-
  pp_probs_allgefs[which(row.names(pp_probs_allgefs) <= the_dates[length(the_dates)]),]


pp_probs_ifs <-
  pp_probs_ifs[which(row.names(pp_probs_ifs) >= the_dates[1]), ]
pp_probs_ifs <-
  pp_probs_ifs[which(row.names(pp_probs_ifs) <= the_dates[length(the_dates)]),]


pp_probs_aifs <-
  pp_probs_aifs[which(row.names(pp_probs_aifs) >= the_dates[1]), ]
pp_probs_aifs <-
  pp_probs_aifs[which(row.names(pp_probs_aifs) <= the_dates[length(the_dates)]),]


pp_probs_allifs <-
  pp_probs_allifs[which(row.names(pp_probs_allifs) >= the_dates[1]), ]
pp_probs_allifs <-
  pp_probs_allifs[which(row.names(pp_probs_allifs) <= the_dates[length(the_dates)]),]


pp_probs_noaa <-
  pp_probs_noaa[which(row.names(pp_probs_noaa) >= the_dates[1]), ]
pp_probs_noaa <-
  pp_probs_noaa[which(row.names(pp_probs_noaa) <= the_dates[length(the_dates)]),]


pp_probs_gem <-
  pp_probs_gem[which(row.names(pp_probs_gem) >= the_dates[1]), ]
pp_probs_gem <-
  pp_probs_gem[which(row.names(pp_probs_gem) <= the_dates[length(the_dates)]),]


pp_probs_allnoaa <-
  pp_probs_allnoaa[which(row.names(pp_probs_allnoaa) >= the_dates[1]), ]
pp_probs_allnoaa <-
  pp_probs_allnoaa[which(row.names(pp_probs_allnoaa) <= the_dates[length(the_dates)]),]


pp_probs_noai <-
  pp_probs_noai[which(row.names(pp_probs_noai) >= the_dates[1]), ]
pp_probs_noai <-
  pp_probs_noai[which(row.names(pp_probs_noai) <= the_dates[length(the_dates)]),]







pp_probs_all$V1 <- c(as_datetime(pp_probs_aifs$V1[1:56]) + hours(3))

pp_probs_gefs$V1 <- c(as_datetime(pp_probs_gefs$V1[1:56]) + minutes(90),as_datetime(pp_probs_gefs$V1[57:84]) + hours(3))
pp_probs_gem$V1 <- c(as_datetime(pp_probs_gem$V1[1:56]) + minutes(90),as_datetime(pp_probs_gem$V1[57:84]) + hours(3))
pp_probs_noaa$V1 <- c(as_datetime(pp_probs_noaa$V1[1:56]) + minutes(90),as_datetime(pp_probs_noaa$V1[57:84]) + hours(3))
pp_probs_aigefs$V1 <- c(as_datetime(pp_probs_aigefs$V1[1:56]) + hours(3))
pp_probs_allgefs$V1 <- c(as_datetime(pp_probs_allgefs$V1[1:56]) + hours(3))
pp_probs_allnoaa$V1 <- c(as_datetime(pp_probs_allnoaa$V1[1:56]) + hours(3))

pp_probs_ifs$V1 <- c(as_datetime(pp_probs_ifs$V1[1:40]) + minutes(90),as_datetime(pp_probs_ifs$V1[41:76]) + hours(3))
pp_probs_noai$V1 <- c(as_datetime(pp_probs_noai$V1[1:40]) + minutes(90),as_datetime(pp_probs_noai$V1[41:76]) + hours(3))
pp_probs_aifs$V1 <- c(as_datetime(pp_probs_aifs$V1[1:56]) + hours(3))
pp_probs_allifs$V1 <- c(as_datetime(pp_probs_allifs$V1[1:56]) + hours(3))

pp_probs_all$V1 <- as.POSIXct(pp_probs_all$V1, tz="UTC")
pp_probs_gefs$V1 <- as.POSIXct(pp_probs_gefs$V1, tz="UTC")
pp_probs_gem$V1 <- as.POSIXct(pp_probs_gem$V1, tz="UTC")
pp_probs_allnoaa$V1 <- as.POSIXct(pp_probs_allnoaa$V1, tz="UTC")
pp_probs_noaa$V1 <- as.POSIXct(pp_probs_noaa$V1, tz="UTC")
pp_probs_aigefs$V1 <- as.POSIXct(pp_probs_aigefs$V1, tz="UTC")
pp_probs_allgefs$V1 <- as.POSIXct(pp_probs_allgefs$V1, tz="UTC")
pp_probs_ifs$V1 <- as.POSIXct(pp_probs_ifs$V1, tz="UTC")
pp_probs_aifs$V1 <- as.POSIXct(pp_probs_aifs$V1, tz="UTC")
pp_probs_allifs$V1 <- as.POSIXct(pp_probs_allifs$V1, tz="UTC")
pp_probs_noai$V1 <- as.POSIXct(pp_probs_noai$V1, tz="UTC")

plotruns$dates <- as_datetime(plotruns$dates)

# norms$DATE <- as_datetime(norms$DATE)

the_dates <- as_datetime(the_dates)




```




```{r prepare_plots}
plot_z500allwai <-
  ggplot(plotruns, aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf(
    "Z500 _ ENS GEFS 00z06z12z18z AIGEFS 00z06z12z18z GEM 00z12z IFS 00z12z AIFS 00z12z  %s",
    date_var
  )) +
  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")


plot_z500allwoai <-
  ggplot(plotruns[which(grepl("^GEFS", plotruns$runs)
                        | grepl("^GEM", plotruns$runs)
                        | grepl("^IFS", plotruns$runs)
                        ),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf(
    "Z500 _ ENS GEFS 00z06z12z18z GEM 00z12z IFS 00z12z  %s",
    date_var
  )) +
  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")


plot_z500gefs <-
  ggplot(plotruns[which(grepl("^GEFS", plotruns$runs)),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf("Z500 _ ENS GEFS 00z06z12z18z  %s", date_var)) +
geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")


plot_z500aigefs <-
  ggplot(plotruns[which(grepl("^AIGEFS", plotruns$runs)),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf("Z500 _ ENS AIGEFS 00z06z12z18z  %s", date_var)) +
geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")


plot_z500allgefs <-
  ggplot(plotruns[which(grepl("GEFS", plotruns$runs)),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf("Z500 _ ENS GEFS 00z06z12z18z AIGEFS 00z06z12z18z  %s", date_var)) +
geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")


plot_z500gem <-
  ggplot(plotruns[which(grepl("^GEM", plotruns$runs)),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf("Z500 _ ENS GEM 00z12z  %s", date_var)) +
geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")


plot_z500noaa <-
  ggplot(plotruns[which(grepl("^GEM", plotruns$runs)
                        |grepl("^GEFS", plotruns$runs)
                        ),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf("Z500 _ ENS GEFS 00z06z12z18z GEM 00z12z  %s", date_var)) +
geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")


plot_z500allnoaa <-
  ggplot(plotruns[which(grepl("^GEM", plotruns$runs)
                        |grepl("^GEFS", plotruns$runs)
                        |grepl("^AIGEFS", plotruns$runs)
                        ),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf("Z500 _ ENS GEFS 00z06z12z18z AIGEFS 00z06z12z18z GEM 00z12z  %s", date_var)) +
geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")




plot_z500ifs <-
  ggplot(plotruns[which(grepl("^IFS", plotruns$runs)),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf("Z500 _ ENS IFS 00z12z  %s", date_var)) +
geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")




plot_z500aifs <-
  ggplot(plotruns[which(grepl("^AIFS", plotruns$runs)),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf("Z500 _ ENS AIFS 00z12z  %s", date_var)) +
geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")




plot_z500allifs <-
  ggplot(plotruns[which(grepl("^AIFS", plotruns$runs)
                        | grepl("^IFS", plotruns$runs)),], aes(dates, geop)) + geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = geop
  )) +
  scale_colour_gradientn(colours = unname(unlist(z500_cols)), limits = c(492, 608)) +
  scale_alpha() + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(480, 620, 20),
    labels = seq(480, 620, 20),
    limits = c(480, 620)
    ,
    sec.axis = sec_axis(
      ~ . ,
      breaks = seq(480, 620, 20),
      labels = seq(480, 620, 20)
    )
  ) + ggtitle(sprintf("Z500 _ ENS IFS 00z12z AIFS 00z12z  %s", date_var)) +
geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "hgt",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")




```

```{r prepare_plots2}




plot_t850allwai <-
  ggplot(plotruns, aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf(
    "T850 + PP _ ENS GEFS 00z06z12z18z AIGEFS 00z06z12z18z GEM 00z12z IFS 00z12z AIFS 00z12z  %s",
    date_var
  ))
idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850allwai <- plot_t850allwai +
    geom_segment(
      data = pp_probs_all,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_all[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}

plot_t850allwai <- plot_t850allwai +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")















plot_t850allwoai <-
  ggplot(plotruns[which(grepl("^GEFS", plotruns$runs)
                        |grepl("^GEM", plotruns$runs)
                        |grepl("^IFS", plotruns$runs)
                        ), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf(
    "T850 + PP _ ENS GEFS 00z06z12z18z GEM 00z12z IFS 00z12z  %s",
    date_var
  ))
idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850allwoai <- plot_t850allwoai +
    geom_segment(
      data = pp_probs_noai,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_ifs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_noai[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}

plot_t850allwoai <- plot_t850allwoai +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")



plot_t850gefs <-
  ggplot(plotruns[which(grepl("^GEFS", plotruns$runs)), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T850 + PP _ ENS GEFS 00z06z12z18z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850gefs <- plot_t850gefs +
    geom_segment(
      data = pp_probs_gefs,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_gefs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_gefs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t850gefs <- plot_t850gefs +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")










plot_t850aigefs <-
  ggplot(plotruns[which(grepl("^AIGEFS", plotruns$runs)), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T850 + PP _ ENS AIGEFS 00z06z12z18z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850aigefs <- plot_t850aigefs +
    geom_segment(
      data = pp_probs_aigefs,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_aigefs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t850aigefs <- plot_t850aigefs +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")










plot_t850allgefs <-
  ggplot(plotruns[which(grepl("GEFS", plotruns$runs)), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T850 + PP _ ENS GEFS 00z06z12z18z AIGEFS 00z06z12z18z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850allgefs <- plot_t850allgefs +
    geom_segment(
      data = pp_probs_allgefs,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_allgefs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t850allgefs <- plot_t850allgefs +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")







plot_t850gem <-
  ggplot(plotruns[which(grepl("^GEM", plotruns$runs)), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T850 + PP _ ENS GEM 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850gem <- plot_t850gem +
    geom_segment(
      data = pp_probs_gem,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_gefs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_gem[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t850gem <- plot_t850gem +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")







plot_t850noaa <-
  ggplot(plotruns[which(grepl("^GEM", plotruns$runs)
                        |grepl("^GEFS", plotruns$runs)), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T850 + PP _ ENS GEFS 00z06z12z18z GEM 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850noaa <- plot_t850noaa +
    geom_segment(
      data = pp_probs_noaa,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_gefs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_noaa[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t850noaa <- plot_t850noaa +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")







plot_t850allnoaa <-
  ggplot(plotruns[which(grepl("^GEM", plotruns$runs)
                        |grepl("GEFS", plotruns$runs)), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T850 + PP _ ENS GEFS 00z06z12z18z AIGEFS 00z06z12z18z GEM 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850allnoaa <- plot_t850allnoaa +
    geom_segment(
      data = pp_probs_allnoaa,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_allnoaa[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t850allnoaa <- plot_t850allnoaa +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")








plot_t850ifs <-
  ggplot(plotruns[which(grepl("^IFS", plotruns$runs)), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T850 + PP _ ENS IFS 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850ifs <- plot_t850ifs +
    geom_segment(
      data = pp_probs_ifs,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_ifs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_ifs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t850ifs <- plot_t850ifs +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")








plot_t850aifs <-
  ggplot(plotruns[which(grepl("^AIFS", plotruns$runs)), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T850 + PP _ ENS AIFS 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850aifs <- plot_t850aifs +
    geom_segment(
      data = pp_probs_aifs,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_aifs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t850aifs <- plot_t850aifs +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")








plot_t850allifs <-
  ggplot(plotruns[which(grepl("IFS", plotruns$runs)), ], aes(dates, tempalt)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-30, 40, 10),
    labels = seq(-30, 40, 10),
    limits = c(-30, 40)
    ,
    sec.axis = sec_axis(
      ~ +(. + 30) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T850 + PP _ ENS IFS 00z12z AIFS 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t850allifs <- plot_t850allifs +
    geom_segment(
      data = pp_probs_allifs,
      aes_string(
        x = "V1",
        y = trans_axes(precip),
        xend = "V1",
        yend = -30
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_allifs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t850allifs <- plot_t850allifs +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempalt
  )) +
  scale_colour_gradientn(colours = unname(unlist(t850_cols)), limits = c(-26, 32)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t850",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")






```

```{r prepare_plots3}



plot_t2mallwai <-
  ggplot(plotruns, aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf(
    "T2M + PP _ ENS GEFS 00z06z12z18z AIGEFS 00z06z12z18z GEM 00z12z IFS 00z12z AIFS 00z12z  %s",
    date_var
  ))
idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2mallwai <- plot_t2mallwai +
    geom_segment(
      data = pp_probs_all,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_all[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t2mallwai <-
  plot_t2mallwai  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")




plot_t2mallwoai <-
  ggplot(plotruns[which(grepl("^GEFS", plotruns$runs)
                        |grepl("^GEM", plotruns$runs)
                        |grepl("^IFS", plotruns$runs)
                        ), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 12),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) +
  scale_x_datetime(expand = c(0, 0),
                   date_breaks = "1 day",
                   date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf(
    "T2M + PP _ ENS GEFS 00z06z12z18z GEM 00z12z IFS 00z12z  %s",
    date_var
  ))
idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2mallwoai <- plot_t2mallwoai +
    geom_segment(
      data = pp_probs_noai,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_ifs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_noai[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}
plot_t2mallwoai <-
  plot_t2mallwoai  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() + geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")











plot_t2mgefs <-
  ggplot(plotruns[which(grepl("^GEFS", plotruns$runs)), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) + scale_x_datetime(expand = c(0, 0),
                       date_breaks = "1 day",
                       date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T2M + PP _ ENS GEFS 00z06z12z18z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2mgefs <- plot_t2mgefs +
    geom_segment(
      data = pp_probs_gefs,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_gefs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_gefs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}



plot_t2mgefs <-
  plot_t2mgefs  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() +  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")























plot_t2maigefs <-
  ggplot(plotruns[which(grepl("^AIGEFS", plotruns$runs)), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) + scale_x_datetime(expand = c(0, 0),
                       date_breaks = "1 day",
                       date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T2M + PP _ ENS AIGEFS 00z06z12z18z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2maigefs <- plot_t2maigefs +
    geom_segment(
      data = pp_probs_aigefs,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_aigefs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}



plot_t2maigefs <-
  plot_t2maigefs  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() +  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")























plot_t2mallgefs <-
  ggplot(plotruns[which(grepl("GEFS", plotruns$runs)), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) + scale_x_datetime(expand = c(0, 0),
                       date_breaks = "1 day",
                       date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T2M + PP _ ENS GEFS 00z06z12z18z AIGEFS 00z06z12z18z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2mallgefs <- plot_t2mallgefs +
    geom_segment(
      data = pp_probs_allgefs,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_allgefs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}



plot_t2mallgefs <-
  plot_t2mallgefs  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() +  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")











plot_t2mgem <-
  ggplot(plotruns[which(grepl("^GEM", plotruns$runs)), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) + scale_x_datetime(expand = c(0, 0),
                       date_breaks = "1 day",
                       date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T2M + PP _ ENS GEM 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2mgem <- plot_t2mgem +
    geom_segment(
      data = pp_probs_gem,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_gefs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_gem[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}



plot_t2mgem <-
  plot_t2mgem  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() +  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")












plot_t2mnoaa <-
  ggplot(plotruns[which(grepl("^GEFS", plotruns$runs)
                        |grepl("^GEM", plotruns$runs)
                        ), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) + scale_x_datetime(expand = c(0, 0),
                       date_breaks = "1 day",
                       date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T2M + PP _ ENS GEFS 00z06z12z18z GEM 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2mnoaa <- plot_t2mnoaa +
    geom_segment(
      data = pp_probs_noaa,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_gefs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_noaa[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}



plot_t2mnoaa <-
  plot_t2mnoaa  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() +  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")












plot_t2mallnoaa <-
  ggplot(plotruns[which(grepl("GEFS", plotruns$runs)
                        |grepl("^GEM", plotruns$runs)
                        ), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) + scale_x_datetime(expand = c(0, 0),
                       date_breaks = "1 day",
                       date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T2M + PP _ ENS GEFS 00z06z12z18z AIGEFS 00z06z12z18z GEM 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2mallnoaa <- plot_t2mallnoaa +
    geom_segment(
      data = pp_probs_allnoaa,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_allnoaa[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}



plot_t2mallnoaa <-
  plot_t2mallnoaa  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() +  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")








plot_t2mifs <-
  ggplot(plotruns[which(grepl("^IFS", plotruns$runs)), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) + scale_x_datetime(expand = c(0, 0),
                       date_breaks = "1 day",
                       date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T2M + PP _ ENS IFS 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2mifs <- plot_t2mifs +
    geom_segment(
      data = pp_probs_ifs,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_ifs,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_ifs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}



plot_t2mifs <-
  plot_t2mifs  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() +  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")








plot_t2maifs <-
  ggplot(plotruns[which(grepl("^AIFS", plotruns$runs)), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) + scale_x_datetime(expand = c(0, 0),
                       date_breaks = "1 day",
                       date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T2M + PP _ ENS AIFS 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2maifs <- plot_t2maifs +
    geom_segment(
      data = pp_probs_aifs,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_aifs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}



plot_t2maifs <-
  plot_t2maifs  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() +  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")








plot_t2mallifs <-
  ggplot(plotruns[which(grepl("IFS", plotruns$runs)), ], aes(dates, tempsol)) + theme_linedraw() + theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.title = element_blank(),
    legend.position = "none",
    panel.background = element_rect(
      fill = "black",
      colour = "black",
      size = 0,
      linetype = "solid"
    ),
    axis.text.x = element_text(angle = 90)
  ) + scale_x_datetime(expand = c(0, 0),
                       date_breaks = "1 day",
                       date_labels = "%d %b",
                   timezone = the_tz,
                   limits = c(the_dates[1], the_dates[1] + days(14))) +
  scale_y_continuous(
    expand = c(0, 0),
    breaks = seq(-20, 50, 10),
    labels = seq(-20, 50, 10),
    limits = c(-20, 50)
    ,
    sec.axis = sec_axis(
      ~ +(. + 20) * 3 / 7,
      breaks = as.numeric(names(pp_cols)),
      labels = names(pp_cols)
    )
  ) + ggtitle(sprintf("T2M + PP _ ENS IFS 00z12z AIFS 00z12z  %s", date_var))

idx <- 110
for (precip in rev(c(seq(0.1, 0.9, 0.1), seq(1, 100)))) {
  plot_t2mallifs <- plot_t2mallifs +
    geom_segment(
      data = pp_probs_allifs,
      aes_string(
        x = "V1",
        y = trans_axes_tsol(precip),
        xend = "V1",
        yend = -20
      ),
      size = barwidth_ai,
      color = MixColor("black", "cornflowerblue", 1 - pp_probs_allifs[, idx]),
      lineend = "butt"
    )
  idx <- idx - 1
}



plot_t2mallifs <-
  plot_t2mallifs  +
  geom_hline(yintercept = 0,
             linetype = "dotted",
             color = "#3c3c3c")  +
  geom_hline(yintercept = 30,
             linetype = "dotted",
             color = "#3c3c3c") +
  geom_count(aes(
    size = ..prop..,
    alpha = ..prop..,
    colour = tempsol
  )) +
  scale_colour_gradientn(colours = unname(unlist(t2m_cols)), limits = c(-16, 50)) +
  scale_alpha() +  geom_line(data = norms_profile [ (norms_profile$date >= the_dates [1]) & (norms_profile$date < (the_dates [1] +days(15)) )
                                                  & norms_profile$type == "t2m",],
                           aes(x = date, y = value, group = 1),
                           color = "gray")










```

# z500/t850 {data-navmenu="ALL woAI — ALL wAI"}


## GEFS - GEM - IFS

### GEFS - GEM - IFS > z500

```{r plot1_72, fig.width=10, fig.height=5}

plot_z500allwoai
```

### GEFS - GEM - IFS > t850 + PP

```{r plot2_72, fig.width=10, fig.height=5}

plot_t850allwoai
```

## GEFS - AIGEFS - GEM - IFS - AIFS

### GEFS - AIGEFS - GEM - IFS - AIFS > z500


```{r plot3_72, fig.width=10, fig.height=5}

plot_z500allwai
```



### GEFS - AIGEFS - GEM - IFS - AIFS + PP

```{r plot4_72, fig.width=10, fig.height=5}

plot_t850allwai
```



# t850/t2m {data-navmenu="ALL woAI — ALL wAI"}

## GEFS - GEM - IFS

### GEFS - GEM - IFS > t850 + PP

```{r plot5_72, fig.width=10, fig.height=5}

plot_t850allwoai
```

### GEFS - GEM - IFS > t2m + PP

```{r plot6_72, fig.width=10, fig.height=5}

plot_t2mallwoai
```

## GEFS - AIGEFS - GEM - IFS - AIFS

### GEFS - AIGEFS - GEM - IFS - AIFS > t850 + PP

```{r plot7_72, fig.width=10, fig.height=5}

plot_t850allwai
```



### GEFS - AIGEFS - GEM - IFS - AIFS > t2m + PP

```{r plot8_72, fig.width=10, fig.height=5}

plot_t2mallwai
```







# z500/t2m {data-navmenu="ALL woAI — ALL wAI"}
## GEFS - GEM - IFS

### GEFS - GEM - IFS > z500

```{r plot9_72, fig.width=10, fig.height=5}

plot_z500allwoai
```

### GEFS - GEM - IFS > t2m + PP

```{r plot10_72, fig.width=10, fig.height=5}

plot_t2mallwoai
```

## GEFS - AIGEFS - GEM - IFS - AIFS

### GEFS - AIGEFS - GEM - IFS - AIFS > z500

```{r plot11_72, fig.width=10, fig.height=5}

plot_z500allwai
```



### GEFS - AIGEFS - GEM - IFS - AIFS > t2m + PP

```{r plot12_72, fig.width=10, fig.height=5}

plot_t2mallwai
```












# z500/t850 {data-navmenu="NOAA-CMC — ECMWF"}


## GEFS - GEM

### GEFS - GEM > z500

```{r plot13_72, fig.width=10, fig.height=5}

plot_z500noaa
```

### GEFS - GEM > t850 + PP

```{r plot14_72, fig.width=10, fig.height=5}

plot_t850noaa
```

## IFS

### IFS > z500


```{r plot15_72, fig.width=10, fig.height=5}

plot_z500ifs
```



### IFS + PP

```{r plot16_72, fig.width=10, fig.height=5}

plot_t850ifs
```



# t850/t2m {data-navmenu="NOAA-CMC — ECMWF"}

## GEFS - GEM

### GEFS - GEM > t850 + PP

```{r plot17_72, fig.width=10, fig.height=5}

plot_t850noaa
```

### GEFS - GEM > t2m + PP

```{r plot18_72, fig.width=10, fig.height=5}

plot_t2mnoaa
```

## IFS

### IFS > t850 + PP

```{r plot19_72, fig.width=10, fig.height=5}

plot_t850ifs
```



### IFS > t2m + PP

```{r plot20_72, fig.width=10, fig.height=5}

plot_t2mifs
```







# z500/t2m {data-navmenu="NOAA-CMC — ECMWF"}
## GEFS - GEM

### GEFS - GEM > z500

```{r plot21_72, fig.width=10, fig.height=5}

plot_z500noaa
```

### GEFS - GEM > t2m + PP

```{r plot22_72, fig.width=10, fig.height=5}

plot_t2mnoaa
```

## IFS

### IFS > z500

```{r plot23_72, fig.width=10, fig.height=5}

plot_z500ifs
```



### IFS > t2m + PP

```{r plot24_72, fig.width=10, fig.height=5}

plot_t2mifs
```




































# z500/t850 {data-navmenu="NOAA-CMC wAI — ECMWF wAI"}


## GEFS - AIGEFS - GEM

### GEFS - AIGEFS - GEM > z500

```{r plot25_72, fig.width=10, fig.height=5}

plot_z500allnoaa
```

### GEFS - AIGEFS - GEM > t850 + PP

```{r plot26_72, fig.width=10, fig.height=5}

plot_t850allnoaa
```

## IFS - AIFS

### IFS - AIFS > z500


```{r plot27_72, fig.width=10, fig.height=5}

plot_z500allifs
```



### IFS - AIFS + PP

```{r plot28_72, fig.width=10, fig.height=5}

plot_t850allifs
```



# t850/t2m {data-navmenu="NOAA-CMC wAI — ECMWF wAI"}

## GEFS - AIGEFS - GEM

### GEFS - AIGEFS - GEM > t850 + PP

```{r plot29_72, fig.width=10, fig.height=5}

plot_t850allnoaa
```

### GEFS - AIGEFS - GEM > t2m + PP

```{r plot30_72, fig.width=10, fig.height=5}

plot_t2mallnoaa
```

## IFS - AIFS

### IFS - AIFS > t850 + PP

```{r plot31_72, fig.width=10, fig.height=5}

plot_t850allifs
```



### IFS - AIFS > t2m + PP

```{r plot32_72, fig.width=10, fig.height=5}

plot_t2mallifs
```







# z500/t2m {data-navmenu="NOAA-CMC wAI — ECMWF wAI"}
## GEFS - AIGEFS - GEM

### GEFS - AIGEFS - GEM > z500

```{r plot33_72, fig.width=10, fig.height=5}

plot_z500allnoaa
```

### GEFS - AIGEFS - GEM > t2m + PP

```{r plot34_72, fig.width=10, fig.height=5}

plot_t2mallnoaa
```

## IFS - AIFS

### IFS - AIFS > z500

```{r plot35_72, fig.width=10, fig.height=5}

plot_z500allifs
```



### IFS - AIFS > t2m + PP

```{r plot36_72, fig.width=10, fig.height=5}

plot_t2mallifs
```























# z500/t850 {data-navmenu="GEFS — IFS"}

## GEFS

### GEFS > z500

```{r plot37_72, fig.width=10, fig.height=5}

plot_z500gefs
```

### GEFS > t850 + PP

```{r plot38_72, fig.width=10, fig.height=5}

plot_t850gefs
```

## IFS

### IFS > z500

```{r plot39_72, fig.width=10, fig.height=5}

plot_z500ifs
```



### IFS > t850 + PP

```{r plot40_72, fig.width=10, fig.height=5}

plot_t850ifs
```



# t850/t2m {data-navmenu="GEFS — IFS"}

## GEFS

### GEFS > t850 + PP

```{r plot41_72, fig.width=10, fig.height=5}

plot_t850gefs
```

### GEFS > t2m + PP

```{r plot42_72, fig.width=10, fig.height=5}

plot_t2mgefs
```

## IFS

### IFS > t850 + PP

```{r plot43_72, fig.width=10, fig.height=5}

plot_t850ifs
```



### IFS > t2m + PP

```{r plot44_72, fig.width=10, fig.height=5}

plot_t2mifs
```







# z500/t2m {data-navmenu="GEFS — IFS"}

## GEFS

### GEFS > z500

```{r plot45_72, fig.width=10, fig.height=5}

plot_z500gefs
```

### GEFS > t2m + PP

```{r plot46_72, fig.width=10, fig.height=5}

plot_t2mgefs
```

## IFS

### IFS > z500

```{r plot47_72, fig.width=10, fig.height=5}

plot_z500ifs
```



### ECMWF > t2m + PP

```{r plot48_72, fig.width=10, fig.height=5}

plot_t2mifs
```
















# z500/t850 {data-navmenu="AIGEFS — AIFS"}

## AIGEFS

### AIGEFS > z500

```{r plot49_72, fig.width=10, fig.height=5}

plot_z500gefs
```

### AIGEFS > t850 + PP

```{r plot50_72, fig.width=10, fig.height=5}

plot_t850allgefs
```

## AIFS

### AIFS > z500

```{r plot51_72, fig.width=10, fig.height=5}

plot_z500aifs
```



### AIFS > t850 + PP

```{r plot52_72, fig.width=10, fig.height=5}

plot_t850aifs
```



# t850/t2m {data-navmenu="AIGEFS — AIFS"}

## AIGEFS

### AIGEFS > t850 + PP

```{r plot53_72, fig.width=10, fig.height=5}

plot_t850allgefs
```

### AIGEFS > t2m + PP

```{r plot54_72, fig.width=10, fig.height=5}

plot_t2mallgefs
```

## AIFS

### AIFS > t850 + PP

```{r plot55_72, fig.width=10, fig.height=5}

plot_t850aifs
```



### AIFS > t2m + PP

```{r plot56_72, fig.width=10, fig.height=5}

plot_t2maifs
```







# z500/t2m {data-navmenu="AIGEFS — AIFS"}

## AIGEFS

### AIGEFS > z500

```{r plot57_72, fig.width=10, fig.height=5}

plot_z500aigefs
```

### AIGEFS > t2m + PP

```{r plot58_72, fig.width=10, fig.height=5}

plot_t2maigefs
```

## AIFS

### AIFS > z500

```{r plot59_72, fig.width=10, fig.height=5}

plot_z500aifs
```



### AIFS > t2m + PP

```{r plot60_72, fig.width=10, fig.height=5}

plot_t2maifs
```




































# z500/t850 {data-navmenu="NOAA wAI — ECMWF wAI"}

## GEFS-AIGEFS

### GEFS-AIGEFS > z500

```{r plot61_72, fig.width=10, fig.height=5}

plot_z500allgefs
```

### GEFS-AIGEFS > t850 + PP

```{r plot62_72, fig.width=10, fig.height=5}

plot_t850allgefs
```

## IFS-AIFS

### IFS-AIFS > z500

```{r plot63_72, fig.width=10, fig.height=5}

plot_z500allifs
```



### IFS-AIFS > t850 + PP

```{r plot64_72, fig.width=10, fig.height=5}

plot_t850allifs
```



# t850/t2m {data-navmenu="NOAA wAI — ECMWF wAI"}

## GEFS-AIGEFS

### GEFS-AIGEFS > t850 + PP

```{r plot65_72, fig.width=10, fig.height=5}

plot_t850allgefs
```

### GEFS-AIGEFS > t2m + PP

```{r plot66_72, fig.width=10, fig.height=5}

plot_t2mallgefs
```

## IFS-AIFS

### IFS-AIFS > t850 + PP

```{r plot67_72, fig.width=10, fig.height=5}

plot_t850allifs
```



### IFS-AIFS > t2m + PP

```{r plot68_72, fig.width=10, fig.height=5}

plot_t2mallifs
```







# z500/t2m  {data-navmenu="NOAA wAI — ECMWF wAI"}

## GEFS-AIGEFS

### GEFS-AIGEFS > z500

```{r plot69_72, fig.width=10, fig.height=5}

plot_z500allgefs
```

### GEFS-AIGEFS > t2m + PP

```{r plot70_72, fig.width=10, fig.height=5}

plot_t2mallgefs
```

## IFS-AIFS

### IFS-AIFS > z500

```{r plot71_72, fig.width=10, fig.height=5}

plot_z500allifs
```



### IFS-AIFS > t2m + PP

```{r plot72_72, fig.width=10, fig.height=5}

plot_t2mallifs
```






























```{r pdf_ens1, echo=F, warning=F, error=F, message=F, results="hide"}
pdf(sprintf("../../data/gefs/ens_unif-%s_%s.pdf",str_replace_all(date_var, "-", ""),prof_name),height=18,width=16)
grid.arrange(plot_z500allwoai,plot_z500gefs,plot_t850allwoai,plot_t850gefs,plot_t2mallwoai,plot_t2mgefs)
dev.off()
```


```{r pdf_ens1ai, echo=F, warning=F, error=F, message=F, results="hide"}
pdf(sprintf("../../data/gefs/ens_ai_unif-%s_%s.pdf",str_replace_all(date_var, "-", ""),prof_name),height=18,width=16)
grid.arrange(plot_z500allwai,plot_z500aigefs,plot_t850allwai,plot_t850aigefs,plot_t2mallwai,plot_t2maigefs)
dev.off()
```






```{r pdf_ens2, echo=F, warning=F, error=F, message=F, results="hide"}
pdf(sprintf("../../data/ifs/ens_unif-%s_%s.pdf",str_replace_all(date_var, "-", ""),prof_name),height=18,width=16)
grid.arrange(plot_z500allwoai,plot_z500ifs,plot_t850allwoai,plot_t850ifs,plot_t2mallwoai,plot_t2mifs)
dev.off()
```




```{r pdf_ens2ai, echo=F, warning=F, error=F, message=F, results="hide"}
pdf(sprintf("../../data/ifs/ens_ai_unif-%s_%s.pdf",str_replace_all(date_var, "-", ""),prof_name),height=18,width=16)
grid.arrange(plot_z500allwai,plot_z500aifs,plot_t850allwai,plot_t850aifs,plot_t2mallwai,plot_t2maifs)
dev.off()
```







```{r load_z500scens}
z500_unif <- allruns[, c(1:3)]
z500_unif <- z500_unif[which(z500_unif$dates >= the_dates[1]), ]

z500_unif <- z500_unif[-which(as.integer(format(as.POSIXct(z500_unif$dates,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]


z500_scens <- cast(na.omit(z500_unif), runs ~ dates)

rownames(z500_scens) <- z500_scens$runs

for (row in 1:nrow(z500_scens)) {
  z500_scens[row, 2:(ncol(z500_scens) - 3)] <-
    na.approx(unlist(z500_scens[row, 2:(ncol(z500_scens) - 3)]), na.rm = FALSE)
}


limit <- 0

if (length(which(is.na(z500_scens[2]))) > 0) {
  z500_scens <- z500_scens[-c(which(is.na(z500_scens[2]))), ]
}

if (length(which(rowSums(is.na(z500_scens[, 2:ncol(z500_scens)])) == ncol(z500_scens) -
                 1)) > 0) {
  z500_scens <-
    z500_scens[-c(which(rowSums(is.na(z500_scens[, 2:ncol(z500_scens)])) == ncol(z500_scens) -
                          1)), ]
}



if (length(which(rowSums(is.na(z500_scens[, 2:(ncol(z500_scens) - 7)])) > 2)) > 0) {
  if (nrow(z500_scens[, 2:(ncol(z500_scens) - 7)]) !=
      nrow(z500_scens[-c(which(rowSums(is.na(z500_scens[, 2:(ncol(z500_scens)
                                                             - 7)])) > 2)), 2:(ncol(z500_scens) - 7)])) {
    z500_scens <-
      z500_scens[-c(which(rowSums(is.na(z500_scens[, 2:(ncol(z500_scens) - 7)])) > 2)), ]
  } else {
    z500_scens[, 2:(ncol(z500_scens) - 7)] <-
      z500_scens[-c(which(rowSums(is.na(z500_scens[, 2:(ncol(z500_scens)
                                                        - 7)])) > 2)), 2:(ncol(z500_scens) - 7)]
  }
}

for (i in seq(ncol(z500_scens) - 1, 1)) {
  if (length(which(rowSums(is.na(z500_scens[, seq(i, ncol(z500_scens))]) *
                           1) == ncol(z500_scens) - i + 1)) == 0) {
    limit <- i
    break
  }
}

z500_scens <- na.omit(z500_scens[, 1:limit])

```












```{r load_t850scens}


t850_unif <- allruns[, c(1, 2, 4)]
t850_unif <- t850_unif[which(t850_unif$dates >= the_dates[1]), ]

t850_unif <- t850_unif[-which(as.integer(format(as.POSIXct(t850_unif$dates,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]

t850_scens <- cast(na.omit(t850_unif), runs ~ dates)

rownames(t850_scens) <- t850_scens$runs

for (row in 1:nrow(t850_scens)) {
  t850_scens[row, 2:(ncol(t850_scens) - 3)] <-
    na.approx(unlist(t850_scens[row, 2:(ncol(t850_scens) - 3)]), na.rm = FALSE)
}


limit <- 0

if (length(which(is.na(t850_scens[2]))) > 0) {
  t850_scens <- t850_scens[-c(which(is.na(t850_scens[2]))), ]
}

if (length(which(rowSums(is.na(t850_scens[, 2:ncol(t850_scens)])) == ncol(t850_scens) -
                 1)) > 0) {
  t850_scens <-
    t850_scens[-c(which(rowSums(is.na(t850_scens[, 2:ncol(t850_scens)])) == ncol(t850_scens) -
                          1)), ]
}


if (length(which(rowSums(is.na(t850_scens[, 2:(ncol(t850_scens) - 7)])) > 2)) > 0) {
  if (nrow(t850_scens[, 2:(ncol(t850_scens) - 7)]) !=
      nrow(t850_scens[-c(which(rowSums(is.na(t850_scens[, 2:(ncol(t850_scens) - 7)])) > 2)), 2:(ncol(t850_scens) - 7)])) {
    t850_scens <-
      t850_scens[-c(which(rowSums(is.na(t850_scens[, 2:(ncol(t850_scens) - 7)])) > 2)),]
  } else {
    t850_scens[, 2:(ncol(t850_scens) - 7)] <-
      t850_scens[-c(which(rowSums(is.na(t850_scens[, 2:(ncol(t850_scens) - 7)])) > 2)), 2:(ncol(t850_scens) - 7)]
  }
}

for (i in seq(ncol(t850_scens) - 1, 1)) {
  if (length(which(rowSums(is.na(t850_scens[, seq(i, ncol(t850_scens))]) *
                           1) == ncol(t850_scens) - i + 1)) == 0) {
    limit <- i
    break
  }
}

t850_scens <- na.omit(t850_scens[, 1:limit])



```














```{r load_ppscens}


pp_unif <- allruns[, c(1, 2, 6)]
pp_unif <- pp_unif[which(pp_unif$dates >= the_dates[1]), ]

pp_unif <- pp_unif[-which(as.integer(format(as.POSIXct(pp_unif$dates,
                                   format = "%Y-%m-%d %H:%M:%S",tz="UTC"),"%H"))  %in% seq(3,21,6)),]

pp_scens <- cast(na.omit(pp_unif), runs ~ dates)

rownames(pp_scens) <- pp_scens$runs

for (row in 1:nrow(pp_scens)) {
  pp_scens[row, 2:(ncol(pp_scens) - 3)] <-
    na.approx(unlist(pp_scens[row, 2:(ncol(pp_scens) - 3)]), na.rm = FALSE)
}

pp_scens <- pp_scens[,-c(2)]

limit <- 0

if (length(which(is.na(pp_scens[2]))) > 0) {
  pp_scens <- pp_scens[-c(which(is.na(pp_scens[2]))), ]
}

if (length(which(rowSums(is.na(pp_scens[, 2:ncol(pp_scens)])) == ncol(pp_scens) -
                 1)) > 0) {
  pp_scens <-
    pp_scens[-c(which(rowSums(is.na(pp_scens[, 2:ncol(pp_scens)])) == ncol(pp_scens) -
                        1)), ]
}


if (length(which(rowSums(is.na(pp_scens[, 2:(ncol(pp_scens) - 7)])) > 2)) > 0) {
  if (nrow(pp_scens[, 2:(ncol(pp_scens) - 7)]) !=
      nrow(pp_scens[-c(which(rowSums(is.na(pp_scens[, 2:(ncol(pp_scens) - 7)])) > 2)), 2:(ncol(pp_scens) - 7)])) {
    pp_scens <-
      pp_scens[-c(which(rowSums(is.na(pp_scens[, 2:(ncol(pp_scens) - 7)])) > 2)),]
  } else {
    pp_scens[, 2:(ncol(pp_scens) - 7)] <-
      pp_scens[-c(which(rowSums(is.na(pp_scens[, 2:(ncol(pp_scens) - 7)])) > 2)), 2:(ncol(pp_scens) - 7)]
  }
}

for (i in seq(ncol(pp_scens) - 1, 1)) {
  if (length(which(rowSums(is.na(pp_scens[, seq(i, ncol(pp_scens))]) * 1) == ncol(pp_scens) -
                   i + 1)) == 0) {
    limit <- i
    break
  }
}

pp_scens <- na.omit(pp_scens[, 1:limit])



```


```{r clustering_funcs}



scens_to_clust <- function(the_unif_scens)
{
  scensx <- repr_matrix(
    the_unif_scens[, -c(1)],
    func = repr_featrend,
    args = list(
      func = maxC,
      pieces = 8,
      order = 12
    ),
    normalise = TRUE,
    func_norm = norm_z
  )
  
  
  clusterings <- lapply(c(2:8), function(x)
    clara(scensx, x))
  
  DB_values <- sapply(seq_along(clusterings), function(x)
    intCriteria(
      scensx,
      as.integer(clusterings[[x]]$clustering),
      c("Davies_Bouldin")
    ))
  
  
  criteriaDB <- unlist(unname(DB_values))
  names(criteriaDB) <- seq(1, length(criteriaDB))
  
  DB_values <- sapply(seq_along(clusterings), function(x)
    intCriteria(scensx, as.integer(clusterings[[x]]$clustering), c("Dunn")))
  
  
  criteriaD <- unlist(unname(DB_values))
  names(criteriaD) <- seq(1, length(criteriaD))
  
  DB_values <- sapply(seq_along(clusterings), function(x)
    intCriteria(
      scensx,
      as.integer(clusterings[[x]]$clustering),
      c("Calinski_Harabasz")
    ))
  
  
  criteriaCH <- unlist(unname(DB_values))
  names(criteriaCH) <- seq(1, length(criteriaCH))
  
  score <- rep(0, length(criteriaDB))
  score[as.integer(names(sort(criteriaDB)))] <-
    score + seq(length(criteriaDB), 1)
  score[as.integer(names(sort(criteriaCH, decreasing = T)))] <-
    score + seq(length(criteriaDB), 1)
  score[as.integer(names(sort(criteriaD, decreasing = T)))] <-
    score + seq(length(criteriaDB), 1)
  names(score) <- seq(2, length(criteriaCH) + 1)
  
  
  
  numb_def <- as.numeric(names(sort(score, decreasing = T)))[1]
  
  
  return(list(numb_def, clusterings, score))
}





cluster_page <- function(name, the_scens, first_page)
  
{
  if (name == "z500") {
    the_breaks = seq(480, 620, 20)
    the_labels = seq(480, 620, 20)
    the_limits = c(480, 620)
    the_norm_type = "hgt"
  }
  
  
  if (name == "t850") {
    the_breaks = seq(-30, 40, 10)
    the_labels = seq(-30, 40, 10)
    the_limits = c(-30, 40)
    the_norm_type = name
  }
  
  
  if (name == "pp") {
    the_breaks = c(seq(0, 1, .5), seq(2, 5, 1), seq(10, 30, 5))
    the_labels = c(seq(0, 1, .5), seq(2, 5, 1), seq(10, 25, 5), "30+")
    the_limits = c(0, 30)
  }
  
  results <- scens_to_clust(the_scens)
  
  numb_def <- results[[1]]
  clusterings <- results[[2]]
  score <- results[[3]]
  
  if (first_page) {
    name <- paste0("Clusters ", name)
  }
  
  for (i in seq(2, 8)) {
    numb <- i
    
    if (numb == numb_def) {
      cat("# Defaut (n=",
          (as.character(numb)),
          ') {data-navmenu="',
          name,
          '"}',
          sep = "")
      
      cat("\n\n")
    } else {
      cat("\n\n")
      cat("# n=",
          (as.character(i)),
          ' {data-navmenu="',
          name,
          '"}',
          sep = "")
      
      cat("\n\n")
    }
    
    
    myplots <- list()
    
    ordre <- clusterings[[numb - 1]]$clusinfo[, 1]
    names(ordre) <- seq(1, length(ordre))
    
    for (clust in seq(1, 8)) {
      myplots[[clust]] <- ggplot()
      if (clust <= numb) {
        elems <-
          which(clusterings[[numb - 1]]$clustering == as.integer(names(sort(
            ordre, decreasing = T
          ))[clust]))
        
        
        the_data <-
          melt(as.data.frame(the_scens[elems, ]), id = c("runs"))
        
        the_data$ID <- the_data$runs
        
        stats <- data.frame(
          DATE = unique(the_data$variable),
          q25 = unname(unlist(lapply(
            the_scens[elems, -c(1)], mean
          ))) - unname(unlist(lapply(
            the_scens[elems, -c(1)], sd
          ))),
          med = unname(unlist(lapply(
            the_scens[elems, -c(1)], mean
          ))),
          q75 = unname(unlist(lapply(
            the_scens[elems, -c(1)], mean
          ))) + unname(unlist(lapply(
            the_scens[elems, -c(1)], sd
          )))
        )
        if (grepl("pp",name)) {
          stats [which(stats$q25 < 0), "q25"] <- 0
          stats [which(stats$q25 > 29.9), "q25"] <- 29.9
          stats [which(stats$med > 29.9), "med"] <- 29.9
          stats [which(stats$q75 > 29.9), "q75"] <- 29.9
          
          
          the_data [which(the_data$value > 29.9), "value"] <- 29.9
        }
        
        the_data$variable <- as_datetime(the_data$variable)
        stats$DATE <- as_datetime(stats$DATE)
        myplots[[clust]] <-
          ggplot(stats, aes(x = DATE)) +
          geom_line(
            data = the_data,
            aes(
              x = variable,
              y = value,
              group = ID
            ),
            alpha = 0.80,
            size = 0.8 ,
            color = "grey30"
          ) +
          geom_ribbon(aes(
            ymin = q25,
            ymax = q75,
            group = 1
          ),
          alpha = 0.60,
          fill = "grey70") +
          geom_line(
            aes(y = med, group = 1),
            alpha = 0.80,
            size = 0.8,
            color = "red"
          ) +
          theme_linedraw() + theme(
            plot.title = element_text(hjust = 0.5, face = "bold"),
            axis.title = element_blank(),
            legend.position = "none",
            panel.background = element_rect(
              fill = "black",
              colour = "black",
              size = 0,
              linetype = "solid"
            ),
            axis.text.x = element_text(angle = 90)
          ) +   scale_x_datetime(
            expand = c(0, 0),
            date_breaks = "1 day",
            date_labels = "%d %b",
            timezone = the_tz,
            limits = c(the_dates[1], the_dates[1] + days(14))
          ) +
          scale_y_continuous(
            expand = c(0, 0),
            breaks =  the_breaks,
            labels =  the_labels,
            limits = the_limits
          ) +
          ggtitle(sprintf(
            "Cluster %s (%s scénarios sur %s)",
            clust,
            length(elems),
            nrow(the_scens)
          ))
        
        if (!grepl("pp",name)) {
          myplots[[clust]] <- myplots[[clust]]  +
            geom_line(
              data = norms_profile [(norms_profile$date >= the_dates [1]) &
                                      (norms_profile$date < (the_dates [1] + days(15)))
                                    &
                                      norms_profile$type == the_norm_type, ],
              aes(
                x = date,
                y = value,
                group = 1
              ),
              color = "white",
              linetype = "dashed"
            )
        }
        
      }
    }
    
    for (j in seq(2, 8, 2)) {
      cat("## Col", as.character(j / 2))
      
      cat("\n\n")
      
      cat("###", name, "> Cluster ", as.character((j - 1)))
      
      cat("\n\n")
      print(myplots[[j - 1]])
      
      cat("\n\n")
      
      cat("###", name, "> Cluster ", as.character((j)))
      
      cat("\n\n")
      print(myplots[[j]])
      
      cat("\n\n")
    }
    
    cat("## Col5")
    
    cat("\n\n")
    
    
    cat("### HeatMap")
    
    cat("\n\n")
    
    
    ze <- c(
      paste(rep(sprintf(
        "GEFS %s sc", format(date_var + hours(0), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 30), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "AIGEFS %s sc", format(date_var + hours(0), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 30), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "IFS %s sc", format(date_var + hours(0), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 50), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "AIFS %s sc", format(date_var + hours(0), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 50), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "GEM %s sc", format(date_var + hours(0), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 20), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "GEFS %s sc", format(date_var + hours(6), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 30), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "AIGEFS %s sc", format(date_var + hours(6), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 30), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "IFS %s sc", format(date_var + hours(6), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 50), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "AIFS %s sc", format(date_var + hours(6), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 50), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "GEM %s sc", format(date_var + hours(6), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 20), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "GEFS %s sc", format(date_var + hours(12), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 30), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "AIGEFS %s sc", format(date_var + hours(12), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 30), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "IFS %s sc", format(date_var + hours(12), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 50), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "AIFS %s sc", format(date_var + hours(12), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 50), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "GEM %s sc", format(date_var + hours(12), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 20), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "GEFS %s sc", format(date_var + hours(18), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 30), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "AIGEFS %s sc", format(date_var + hours(18), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 30), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "IFS %s sc", format(date_var + hours(18), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 50), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "AIFS %s sc", format(date_var + hours(18), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 50), 2, pad = "0"), sep = ""),
      paste(rep(sprintf(
        "GEM %s sc", format(date_var + hours(18), "%Y-%m-%d %H:%M:%S")
      )), str_pad(seq(1, 20), 2, pad = "0"), sep = "")
    )
    ze_s <- c(
      paste("00z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 30), 2, pad = "0"), sep = ""),
      paste("00z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 30), 2, pad = "0"), sep = ""),
      paste("00z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 50), 2, pad = "0"), sep = ""),
      paste("00z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 50), 2, pad = "0"), sep = ""),
      paste("00z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 20), 2, pad = "0"), sep = ""),
      paste("06z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 30), 2, pad = "0"), sep = ""),
      paste("06z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 30), 2, pad = "0"), sep = ""),
      rep("", 50 * 2 + 20),
      paste("12z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 30), 2, pad = "0"), sep = ""),
      paste("12z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 30), 2, pad = "0"), sep = ""),
      paste("12z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 50), 2, pad = "0"), sep = ""),
      paste("12z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 50), 2, pad = "0"), sep = ""),
      paste("12z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 20), 2, pad = "0"), sep = ""),
      paste("18z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 30), 2, pad = "0"), sep = ""),
      paste("18z sc", str_pad(seq(1, 1), 2, pad = "0"), sep = ""),
      paste(rep("    sc"), str_pad(seq(2, 30), 2, pad = "0"), sep = ""),
      rep("", 50 * 2 + 20)
    )
    
    cl <- rep(NA, (30 * 2 * 4) + (20 * 4) + (50 * 2 * 4))
    
    for (clust in seq(1, numb)) {
      elems <-
        which(clusterings[[numb - 1]]$clustering == as.integer(names(sort(
          ordre, decreasing = T
        ))[clust]))
      cl[match(row.names(the_scens[elems, ]), ze)] <- clust
    }
    
    map <- data.frame(SCENS = ze, CLUST = as.factor(cl))
    
    
    a <-
      ggplot(map[which(str_detect(map[, 1], "^GEFS")), ], aes(x = 1, y = rev(SCENS))) +
      geom_tile(aes(fill = CLUST)) + theme_linedraw() + theme(
        panel.grid.major = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_blank(),
        legend.position = "right"
      ) +
      scale_fill_manual(
        limits = factor(c(1:numb)),
        values = brewer.pal(n = 12, name = "Paired")[1:numb],
        name = "Clusters"
      ) + scale_x_continuous(expand = c(0, 0), breaks = c()) + scale_y_discrete(labels =
                                                                                  rev(ze_s[which(str_detect(map[, 1], "^GEFS"))])) + ggtitle("GEFS")
    
    
    a_ai <-
      ggplot(map[which(str_detect(map[, 1], "AIGEFS")), ], aes(x = 1, y = rev(SCENS))) +
      geom_tile(aes(fill = CLUST)) + theme_linedraw() + theme(
        panel.grid.major = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_blank(),
        legend.position = "right"
      ) +
      scale_fill_manual(
        limits = factor(c(1:numb)),
        values = brewer.pal(n = 12, name = "Paired")[1:numb],
        name = "Clusters"
      ) + scale_x_continuous(expand = c(0, 0), breaks = c()) + scale_y_discrete(labels =
                                                                                  rev(ze_s[which(str_detect(map[, 1], "AIGEFS"))])) + ggtitle("AIGEFS")
    
    b <-
      ggplot(map[which(str_detect(map[, 1], "^IFS")), ], aes(x = 1, y = rev(SCENS))) +
      geom_tile(aes(fill = CLUST)) + theme_linedraw() + theme(
        panel.grid.major = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_blank(),
        legend.position = "right"
      ) +
      scale_fill_manual(
        limits = factor(c(1:numb)),
        values = brewer.pal(n = 12, name = "Paired")[1:numb],
        name = "Clusters"
      ) + scale_x_continuous(expand = c(0, 0), breaks = c()) + scale_y_discrete(labels =
                                                                                  rev(ze_s[which(str_detect(map[, 1], "^IFS"))])) + ggtitle("IFS")
    
    b_ai <-
      ggplot(map[which(str_detect(map[, 1], "AIFS")), ], aes(x = 1, y = rev(SCENS))) +
      geom_tile(aes(fill = CLUST)) + theme_linedraw() + theme(
        panel.grid.major = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_blank(),
        legend.position = "right"
      ) +
      scale_fill_manual(
        limits = factor(c(1:numb)),
        values = brewer.pal(n = 12, name = "Paired")[1:numb],
        name = "Clusters"
      ) + scale_x_continuous(expand = c(0, 0), breaks = c()) + scale_y_discrete(labels =
                                                                                  rev(ze_s[which(str_detect(map[, 1], "AIFS"))])) + ggtitle("AIFS")
    
    c <-
      ggplot(map[which(str_detect(map[, 1], "GEM")), ], aes(x = 1, y = rev(SCENS))) +
      geom_tile(aes(fill = CLUST)) + theme_linedraw() + theme(
        panel.grid.major = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title = element_blank(),
        legend.position = "right"
      ) +
      scale_fill_manual(
        limits = factor(c(1:numb)),
        values = brewer.pal(n = 12, name = "Paired")[1:numb],
        name = "Clusters"
      ) + scale_x_continuous(expand = c(0, 0), breaks = c()) + scale_y_discrete(labels =
                                                                                  rev(ze_s[which(str_detect(map[, 1], "GEM"))])) + ggtitle("GEM")
    
    
    myplots[[9]] <-
      ggarrange(
        a,
        a_ai,
        b,
        b_ai,
        c,
        ncol = 5,
        common.legend = TRUE,
        legend = "bottom"
      )
    print(myplots[[9]])
    
    cat("\n\n")
    
    
    cat("### Tracé d'effondrement")
    
    cat("\n\n")
    
    
    myplots[[10]] <-
      ggplot(data.table(Clusters = 2:8, Scores = -unlist(score)),
             aes(Clusters, Scores)) +
      geom_line(size = 1) +
      geom_point(size = 3) +
      theme_bw() + scale_x_continuous(breaks = seq(2, 8)) + theme_linedraw() + theme(plot.title = element_text(hjust = 0.5, face = "bold")) + ggtitle("pp")
    print(myplots[[10]])
    
    cat("\n\n")
    
    
    
    if (numb == numb_def) {
      defplots <- myplots
    }
    
    
  }
  
  return(defplots)
}



```







```{r cluster_page_gen, results="asis"}


myplots_z500 <- cluster_page("z500",z500_scens,TRUE)

myplots_t850 <- cluster_page("t850",t850_scens,TRUE)


myplots_pp <- cluster_page("pp",pp_scens,TRUE)



```





```{r pdf_clust, echo=F, warning=F, error=F, message=F, results="hide"}

pdf(
  sprintf(
    "../../data/gefs/ens_cluster_unif-%s_%s.pdf",
    str_replace_all(date_var, "-", ""), prof_name
  ),
  height = 23,
  width = 15
)
do.call(grid.arrange, c(myplots_z500, ncol = 2, nrow = 5))
do.call(grid.arrange, c(myplots_t850, ncol = 2, nrow = 5))
do.call(grid.arrange, c(myplots_pp, ncol = 2, nrow = 5))
dev.off()


```


